The Eclipse Integrated Computational Environment

### 2017-05-23 src/main.tex
Fixed messed up superscripts in affiliations. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\address{$^1$Computer Science and Mathematics Division, Oak Ridge National
Laboratory, Oak Ridge, TN 37830, USA}
\address{$^2$The Bredesen Center for Interdisciplinary Research and Graduate
Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
  Blvd. Knoxville, TN 37996-3394}
\address{$^3$University of Washington, Seattle, WA 98105}
\address{$^4$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
53188-1678}
\address{$^5$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
\address{$^6$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
HP13 5LN United Kingdom}
\address{$^7$Northwestern University 633 Clark Street Evanston, IL 60208}
\address{$^8$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
CA 94720}
\address{$^9$Department of Computer Science, and Department of Biological
Sciences, Purdue University, West Lafayette, IN 47906} 
\address{$^10$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
TN 37830}
\address{$^11$Colorado State University Fort Collins, CO 80523}

>>>>

\address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National
Laboratory, Oak Ridge, TN 37830, USA}
\address{$^{2}$The Bredesen Center for Interdisciplinary Research and Graduate
Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
  Blvd. Knoxville, TN 37996-3394}
\address{$^{3}$University of Washington, Seattle, WA 98105}
\address{$^{4}$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
53188-1678}
\address{$^{5}$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
\address{$^{6}$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
HP13 5LN United Kingdom}
\address{$^{7}$Northwestern University 633 Clark Street Evanston, IL 60208}
\address{$^{8}$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
CA 94720}
\address{$^{9}$Department of Computer Science, and Department of Biological
Sciences, Purdue University, West Lafayette, IN 47906} 
\address{$^{10}$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
TN 37830}
\address{$^{11}$Colorado State University Fort Collins, CO 80523}
